---
title: "Daily Wellbeing Dashboard"
# author: "Jordan Hutchings"
# date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
 flexdashboard::flex_dashboard:
   css: styles.css
   orientation: rows
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warnings = FALSE, 
                      messages = FALSE)

pacman::p_load(googlesheets4, ggplot2, dplyr)
source("../secrets.R")

# ggplot theme
theme_set(
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(), 
    # axis.ticks.y = element_blank(),
    plot.title=element_text(size = 16, face="bold"),
    plot.title.position = "plot",
    plot.subtitle=element_text(face="italic", size=12, margin=margin(b=12)),
    plot.caption=element_text(size=8, margin=margin(t=8), color="#7a7d7e"), 
    legend.position = "bottom"
    )
)

# toggle the eval argument of code chunks, to preview blog post w/o code
# Use: ```{r, eval = RUN_CODE}
RUN_CODE = FALSE
```

# Blog Post

I had some down time before beginning the summer math camp for my 
PhD, and decided it would be a good idea to begin tracking my 
personal wellbeing throughout my PhD. 

There were a couple key factors I wanted to include in my tracking progress: 

1. **Ease of use** - I wanted an application that I would be able to do on days where I didn't feel like doing anything. I decided to use `cronR` to automate a script that would send the survey link to my phone each morning. Paired with `pushoverr`, I now receive a push notification each morning that opens a Google Form containing one page of questions on my mental wellbeing. The entire process start to finish takes less than a minute to complete. 

2. **Configurable** - I want to create a question bank of information specific to myself which I would like to track. For this reason, I decided to avoid any pre-made apps. Google Forms allowed me to make my own survey to track the questions I am most interested in. Additionally, the google form automatically saves all entered information into a Google Sheet, which can easily be read into R for further analysis. 

3. **Reproducible** - I want to be able to make the information easy to share with others. The code base for the log is written in R Markdown, with the only external resource being Google Forms. This makes the project very easy for others to adopt. 


**Creating the tracker**

I followed these four steps to create my wellbeing tracker: 

1. Create a Google Form with the information you want to track. 
    * Collect the Google Form URL, this will be the URL we embed in our push notification. 
    * In results, click "View in Sheets", collect this URL as well, as it will be where we collect the response data. 
2. Set up a Pushover API to receive push notifications on your phone. 
    * install the `pushoverr` R library. 
    * install the Pushover app on your phone. 
    * create a Pushover application at [pushover.net](https://pushover.net/). This will provide a `USER_KEY`, and `API_KEY` needed for sending push notifications from R. 
    * For more info setting up Pushover, see Brian Connelley's blog post [R Phone Home: Notifications with pushoverr](https://bconnelly.net/posts/r-phone-home/).
3. Write R code to send push notifications. 
    
    ```{r, eval = FALSE}
    # file name: send-push.R
    
    USER_KEY = "YYYYY"
    APP_KEY = "ZZZZZ"
    GOOGLE_FORM_URL = "XXXXX"
    
    pushoverr::pushover(message = "Enter your daily wellbeing information", 
                        user = USER_KEY, 
                        app = APP_KEY, 
                        url = GOOGLE_FORM_URL, 
                        url_title = "Wellbeing Link")
    
    ```
4. Schedule the R code to run daily.
    * I used `cronR` to schedule the send-push.R to run daily at 8:15am. 
    * This can be scheduled using `cronR::cron_add()`, or with the RStudio cronR addin "Schedule R Scripts on Linux/Unix". 
        * cronR is Linux/Unix based. For Windows machines, look to Task Scheduler or other automation processes. 

For more information, you can my Daily Wellbeing repository [here](https://github.com/jjhutchi/daily-wellbeing-log). 

# Viz

```{r, warning=FALSE, message=FALSE, include=FALSE, eval=RUN_CODE}
data = googlesheets4::read_sheet(GOOGLE_SHEET)
data |> 
  head()
```

## Row {data-height="600"}

### Plot of overall wellbeing

```{r, echo=FALSE, eval=RUN_CODE}
data |>
  mutate(date = as.Date(Timestamp),
           caffine_intake = substr(wellbeing_score, 1, 2)) |>
  ggplot(aes(x = date, y = wellbeing_score)) +
  geom_point()
```

## Row {data-height="350"}

### Caffine Consumption

```{r, echo=FALSE, eval=RUN_CODE}
data |>
    mutate(date = as.Date(Timestamp),
           caffine_intake = substr(caffine_intake, 1, 2)) |>
    ggplot(aes(x = date, y = caffine_intake)) +
    geom_point()
```

### Overall Perceived Sleep

```{r, echo=FALSE, eval=RUN_CODE}
data |>
    mutate(date = as.Date(Timestamp),
           sleep_score = substr(sleep_score, 1, 2)) |>
    ggplot(aes(x = date, y = sleep_score)) +
    geom_point()
```
